---
title: "Resultados"
author: "Cristiano Santos"
date: "20 de abril de 2018"
output: 
  word_document: 
    fig_height: 10
    fig_width: 8
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
load("resultados.RData")
source("R/functions.R")
library(ggplot2)
```

## Resultados


```{r fig1, echo=FALSE}
colnames(mY) <- c("PIB", 
                  "Inflação", 
                  "Juros real", 
                  "desemprego")
p <- tsplot(mY, mnr_med)
p <- p + annotate("rect", xmin=mTP$Trough, xmax=mTP$Peak,
                  ymin=-Inf, ymax=Inf, alpha=.2, fill="red")
p 
```

Fig. 1 Actual and natural rates. The solid line is the actual rate; the dashed line is the natural rate. The shaded areas indicate the NBER recessions



```{r fig2, echo=FALSE}
colnames(mgap_med) <- c("PIB", 
                  "inflação", 
                  "juros real", 
                  "desemprego")
p <- bitsplot(x = mgap_med, lower = mgap_lower, upper = mgap_upper)
p <- p + annotate("rect", xmin=mTP$Trough, xmax=mTP$Peak,
                  ymin=-Inf, ymax=Inf, alpha=.2, fill="red")
p <- p + theme(panel.grid.major.y = element_blank(),
panel.grid.minor.y = element_blank())
p <- p + geom_hline(yintercept = 0, size = 0.2)
p
```

Fig. 2 Gaps. The dashed lines are the 0.025- and 0.975-quantiles. The shaded areas indicate the NBER recessions


```{r fig3, echo=FALSE}

library(gridExtra)
p1 <- DrawScatter(mgap_med, "PIB", "inflação")
p2 <- DrawPDF(amcorr[2, 1,], "coeficiente de correlação")
p3 <- DrawScatter(mgap_med, "desemprego", "inflação")
p4 <- DrawPDF(amcorr[2, 4,], "coeficiente de correlação")
p5 <- DrawScatter(mgap_med, "desemprego", "PIB")
p6 <- DrawPDF(amcorr[1, 4,], "coeficiente de correlação")

grid.arrange(p1, p2, p3, p4, p5, p6, ncol=2)
```

Fig. 3 Phillips curve andOkun’s law.The left panels are the scatter plots of the simulated posteriormedians of the gaps in each quarter; the right panels are the simulated posterior pdfs of the correlation coefficients between the gaps


```{r fig4, echo=FALSE}
colnames(mgapDI) <- c("PIB", 
                  "Inflação", 
                  "Juros real", 
                  "desemprego")
p <- tsplot(mgapDI)
p <- p + annotate("rect", xmin=mTP$Trough, xmax=mTP$Peak,
                  ymin=-Inf, ymax=Inf, alpha=.2, fill="red")
p <- p + theme(panel.grid.major.y = element_blank(),
panel.grid.minor.y = element_blank())
p <- p + geom_hline(yintercept = 0.5, size = 0.2)
p 
```


Fig. 4 Posterior probability of positive gap. The shaded areas indicate the NBER recessions


```{r fig5, echo=FALSE}
colnames(mets) <- c("PIB", 
                  "Inflação", 
                  "Juros real", 
                  "desemprego")
p <- tsplot(mets)
p <- p + annotate("rect", xmin=mTP$Trough, xmax=mTP$Peak,
                  ymin=-Inf, ymax=Inf, alpha=.2, fill="red")
p <- p + theme(panel.grid.major.y = element_blank(),
panel.grid.minor.y = element_blank())
p <- p + geom_hline(yintercept = 0.5, size = 0.2)
p 
```

Fig. 5 Posterior probability of recession. The shaded areas indicate the NBER recessions


```{r fig6, echo=FALSE}
colnames(mcts) <- c("PIB", 
                  "Inflação", 
                  "Juros real", 
                  "desemprego")
p <- tsplot(mcts)
p <- p + annotate("rect", xmin=mTP$Trough, xmax=mTP$Peak,
                  ymin=-Inf, ymax=Inf, alpha=.2, fill="red")
p <- p + theme(panel.grid.major.y = element_blank(),
panel.grid.minor.y = element_blank())
p <- p + geom_hline(yintercept = 0.5, size = 0.2)
p 
```


Fig. 6 Posterior probability of revival. The shaded areas indicate the NBER recessions

